Devito for large scale elastic modelling and anisotropic inversion

### 2020-04-21 paper.tex
minor polishing

Devito \cite{devito-api} provides a functional language built on top of
\texttt{SymPy} \cite{sympy} to symbolically express PDEs at a
mathematical level and implements automatic discretization with the
finite-difference method. The language is by design flexible enough to
express other types of non finite-diffrence operators, such as
interpolation and tensor contractions, that are inherent to
measurement-based inverse problems. Several additional features are
supported, among which staggered grids, sub-domains, and stencils with
custom coefficients. The last major building block of a good PDE solver
are the boundary conditions, that for finite-difference methods are
notoriously various and often complicated. The system is, however,
sufficiently general to express them through composition of core
mechanisms. For example, free surface and perfectly-matched layers
(PMLs) boundary conditions can be expressed as equations -- just like
any other PDE equations -- over a suitable sub-domain.

@@

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  \texttt{Grid}, a representation of the discretized model.
\item
  \texttt{(Time)Function}, a representation of spatially (and time-)
  varying variables defined on a \texttt{Grid} object.
\item
  \texttt{Sparse(Time)Function} a represention of (time-varying) point
  objects on a \texttt{Grid} object, generally unaligned with respect to
  the grid points, hence called ``sparse''.
\end{itemize}

@@

The source term is handled separately from the PDE as a pointwise
operation called \texttt{injection}, while the measurement is handled
with an interpolation. By default,
\href{https://github.com/devitocodes/devito}{Devito} initializes all
\texttt{Function} data to 0, and thus automatically satisfies the zero
Dirichlet condition at \texttt{t=0}. The isotropic acoustic
wave-equation can then be implemented in
\href{https://github.com/devitocodes/devito}{Devito} as below

>>>>

Devito \cite{devito-api} provides a functional language built on top of
\texttt{SymPy} \cite{sympy} to symbolically express PDEs at a
mathematical level and implements automatic discretization with the
finite-difference method. The language is by design flexible enough to
express other types of non finite-difference operators, such as
interpolation and tensor contractions, that are inherent to
measurement-based inverse problems. Several additional features are
supported, among which staggered grids, sub-domains, and stencils with
custom coefficients. The last major building block of a good PDE solver
are the boundary conditions, that for finite-difference methods are
notoriously various and often complicated. The system is, however,
sufficiently general to express them through composition of core
mechanisms. For example, free surface and perfectly-matched layers
(PMLs) boundary conditions can be expressed as equations -- just like
any other PDE equations -- over a suitable sub-domain.

@@

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  \texttt{Grid}, a representation of the discretized model.
\item
  \texttt{(Time)Function}, a representation of spatially (and time-)
  varying variables defined on a \texttt{Grid} object.
\item
  \texttt{Sparse(Time)Function} a representation of (time-varying) point
  objects on a \texttt{Grid} object, generally unaligned with respect to
  the grid points, hence called ``sparse''.
\end{itemize}

@@

The source term is handled separately from the PDE as a pointwise
operation called injection, while the measurement is handled
with an interpolation. By default,
\href{https://github.com/devitocodes/devito}{Devito} initializes all
\texttt{Function} data to 0, and thus automatically satisfies the zero
Dirichlet condition at \texttt{t=0}. The isotropic acoustic
wave-equation can then be implemented in
\href{https://github.com/devitocodes/devito}{Devito} as below
